Kyoto VR MQP Paper First Draft

### 2019-09-24 paper.tex
fixed broken references

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process, which can be seen in
Figure~\ref{ref:uploadingMessage}. If a 200 or 201 is returned from the server,
a ``Success'' message will appear. If there was some problem, the error message
returned by the server is displayed in this box instead. Since uploading,
downloading and deleting are all network-related operations, it makes sense to
include this message box for each card.

@@

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. The download
card containing a box filled with filenames on the server can be seen in
Figure~\ref{download-card-editour.png}.

>>>>

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process, which can be seen in
Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
a ``Success'' message will appear. If there was some problem, the error message
returned by the server is displayed in this box instead. Since uploading,
downloading and deleting are all network-related operations, it makes sense to
include this message box for each card.

@@

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. The download
card containing a box filled with filenames on the server can be seen in
Figure~\ref{fig:downloadCard}.
